---
title: "Guppy Foraging Mansucript Data Analysis"
author: "Lauren E Johnson"
date: "06/1/2022"
output: html_document
---

```{r setup, include=FALSE}
#library(learn.plasticity)
library(tidyverse)
library(MASS)
library(knitr)
opts_chunk$set(echo = TRUE)
```

**Model selection function:** Perform model selection on a specified full model (LM, LMM, GLM, GLMM) by calculating the AICs and producing a table of the best models within a given deltaAIC. It also gives the final/reduced model as the model, within those, that has the most parameters and lowest AIC. Model selection is done sequentially using function MuMIn::dredge.
```{r}
model_selection <- function (model, delta = 2){

  # Model selection
  AICtable_full <- MuMIn::dredge(model)

  top_models_index <- which(AICtable_full[,'delta'] <= delta)
  AICtable <- AICtable_full[top_models_index,]

  model_list <-MuMIn::get.models(AICtable, subset = delta <= delta)

  final_model_index <- which.max(unlist(lapply(lapply(model_list, coefficients), length)))

  final_model <- model_list[[final_model_index]]

  return(list(AIC_table = AICtable,
              final_model = final_model))
}

```

Import data:  
```{r}
#make_forage()
load(file = paste0(here::here('data'),'/data_forage.Rda'))

kable(head(data_forage))
```

Remove AHF2_1O3P.1.3 and AHF2_1O3P.1.4 because they were assessed at 76 and 77 days old
```{r}

data_forage <- data_forage[!data_forage$ID =="AHF2_1O3P.1.3",]

data_forage <- data_forage[!data_forage$ID =="AHF2_1O3P.1.4",]

#data_forage <- data_forage[data_forage$ID =="AHF2_1O3P.1.3",]

#data_forage <- data_forage[data_forage$ID =="AHF2_1O3P.1.4",]

#data_forage %>%  filter(ID=='AHF2_1O3P.1.3' | ID=='AHF2_1O3P.1.4')

# THis isn't working, I'll just manually delete these guys!
```

Ben Bolker (creater of LME4) recommends using glmmTMB instead of lme4::glmer.nb for negative binomial GLMMs. Nevertheless, he said that is smart to check model parameters with different implementations/algorithms to make sure the answers are consistent - he calls it the gold standard for addressing convergence warnings, so that is what we are going to do!
```{r}
# data_f <- data_forage %>%
#   filter(Sex == 'F') %>%
#   na.omit
# 
# library(lme4)
# m1 <- glmer.nb(Attempts ~ (Population + Pred + Tutor_pop + Water)^2 + (1|ID) + (1|Mom_ID), data = data_f,  na.action = "na.fail", family = poisson(), control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
# # Fails to converge, but outpute suggests that it could be false +
# 
# library(glmmTMB)
# m2 <- glmmTMB(Attempts ~ (Population + Pred + Tutor_pop + Water)^2 + (1|ID) + (1|Mom_ID), na.action = "na.fail", family = 'nbinom2', data = data)
# 
# library(ggplot2)
# library(dotwhisker)
# library(broom.mixed) 
# dwplot(list(glmer.nb=model1,glmmTMB=model),effect="fixed") + theme_bw() +
#     geom_vline(xintercept=0,lty=2)

```
Coefficients are similar, so either either output could be used. But let's continue with the glmmTMB since Bolker recommends that...

#### **Sibling Summary**
```{r}
sibs <- table(data_forage$Mom_ID)
sibs <- sibs/2 #accounting for fact that there are 2 entries for each individual 
sibs

kable(sibs)
library(ggplot2)
sibplot <- ggplot(data_forage, aes(x=(Mom_ID), fill = Pred_Tutor)) +
    geom_bar() + theme(axis.text.x = element_text(angle = 90))  # going to renumber the axis tickmarks in illustrator (needs to be half )

sibplot
```

#### **Foraging Attempts Analyses**  

##### **Female Foraging Attempts**  

1. Subset female data  
```{r}
data <- data_forage %>% filter(Sex == 'F') %>% na.omit

#sample size
n_distinct(data$ID)
```

2. Create generalized linear mixed model with all interactions
```{r message=FALSE, warning=FALSE}
library(glmmTMB)
model_pecks <- glmmTMB(Attempts ~ (Population + Pred + Tutor_pop + Water)^2 + (1|ID) + (1|Mom_ID), na.action = "na.fail", family = 'nbinom2', data = data)
```

3. Run model selection (Andres's model selection function does not work with the glmmTMB, so need to do model selection manually by look at the AIC_table)
```{r}
mp <- glmmTMB(Attempts ~ Population + Pred + Tutor_pop + Water + Population:Pred + Population:Water + Pred:Water + Tutor_pop:Water + (1|ID) + (1|Mom_ID), na.action = "na.fail", family = 'nbinom2', data = data)
```

```{r}
dotwhisker::dwplot(mp, effects = "fixed") + geom_vline(xintercept=0,lty=2) + xlab("Coefficient")
```
4. Summary of final **generalized linear mixed model** for female foraging attempts

```{r}
a1 <- car::Anova(mp, type = 'III')

kable(a1)
kable(summary(mp)$coefficients)
```

##### **Male Foraging Attempts**  

1. Subset male data
```{r}
data2 <- data_forage %>% filter(Sex == 'M') %>% na.omit
n_distinct(data2$ID)
```

2. Create generalized linear mixed model with all interactions
```{r}
model_pecks2 <- glmmTMB(Attempts ~ (Population + Pred + Tutor_pop + Water)^2 + (1|ID) + (1|Mom_ID), na.action = "na.fail", family = 'nbinom2', data = data2)
```

3. Run model selection (Andres's model selection function does not work with the glmmTMB, so need to do model selection manually by look at the AIC_table)
```{r}
mp2 <- glmmTMB(Attempts ~ Population + Tutor_pop + Water + Population:Water + Tutor_pop:Water + (1|ID) + (1|Mom_ID), na.action = "na.fail", family = 'nbinom2', data = data2)
```

```{r}
dotwhisker::dwplot(mp2, effects = "fixed") + geom_vline(xintercept=0,lty=2)
```

4. Summary of final **generalized linear mixed model** for male foraging attempts

```{r}
a2 <- car::Anova(mp2, type = 'III')

kable(a2)
kable(summary(mp2)$coefficients)
```

Note that it is important to remove `NA`s (with `na.omit`) and set `na.action = "na.fail"` so that the AIC works with models that have the exact same number of datapoints.

Now we can use our home-made function `model_selection`.

#### **Latency Analyses**

##### **Female Latency**  

1. Subset female data  
```{r}
data <- data_forage %>% filter(Sex == 'F') %>% na.omit
```

2. Create Cox proportional hazards model with all interactions  
```{r message=FALSE, warning=FALSE}
library(coxme)

ml1 <- coxme(Surv(Latency, event = event) ~ (Population + Pred + Tutor_pop + Water)^2 + (1|ID) + (1|Mom_ID), data = data, na.action = 'na.fail')
```

3. Run model selection  
```{r}
models_ml1 <- model_selection(ml1)

kable(models_ml1$AIC_table)
```

```{r}
dotwhisker::dwplot(models_ml1$final_model, effects = "fixed") + geom_vline(xintercept=0,lty=2) + xlab("Coefficient")
```

4. Summary of final **cox proportional hazards mixed model summary** for female foraging latency  

```{r}
anova <- car::Anova(models_ml1$final_model, type = 'III')
summary(models_ml1$final_model)

kable(anova)
```

##### **Male Latency**  

1. Subset male data  
```{r}
data2 <- data_forage %>% filter(Sex == 'M') %>% na.omit
```

2. Create Cox proportional hazards model with all interactions  
```{r}
ml2 <- coxme(Surv(Latency, event = event) ~ (Population + Pred + Tutor_pop + Water)^2 + (1|ID) + (1|Mom_ID), data = data2, na.action = 'na.fail')
```

3. Run model selection  
```{r}
models_ml2 <- model_selection(ml2)

kable(models_ml2$AIC_table)
```

```{r}
dotwhisker::dwplot(models_ml2$final_model, effects = "fixed") + geom_vline(xintercept=0,lty=2) + xlab("Coefficient")

```

4. Summary of final **cox proportional hazards mixed model summary** for male foraging latency  
```{r}
anova2 <- car::Anova(models_ml2$final_model, type = 'III')
summary(models_ml2$final_model)

kable(anova2)
```


### **Post-hoc analyses**

Male Latency
```{r}
library(emmeans)

ML <- coxph(models_ml2$final_model$formulaList$fixed, data = data2, na.action = 'na.fail')

emmML1 <- emmeans(ML, specs = pairwise ~ Population:Pred)
emmML2 <- emmeans(ML, specs = pairwise ~ Population|Pred)
emmML3 <- emmeans(ML, specs = pairwise ~ Pred|Population)

emmML1$emmeans
emmML2$emmeans
emmML3$emmeans
```

Male Foraging Attempts:
```{r}
emmMF1 <- emmeans(model_pecks2, ~Tutor_pop:Water) %>% pairs() %>% test(by = NULL, adjust = "sidak")
emmMF2 <- emmeans(model_pecks2, ~Tutor_pop|Water) %>% pairs() %>% test(by = NULL, adjust = "sidak")
emmMF3 <- emmeans(model_pecks2, ~Water|Tutor_pop)%>% pairs() %>% test(by = NULL, adjust = "sidak")

emmMF1$emmeans
emmMF2$emmeans
emmMF3$emmeans

emmMF1
emmMF2
emmMF3
```

Female Foraging Attempts:
```{r}
emmFF1 <- emmeans(model_pecks, specs = pairwise~Water:Pred)
emmFF2 <- emmeans(model_pecks, specs = pairwise~Water|Pred)
emmFF3 <- emmeans(model_pecks, ~Pred|Water) %>% pairs() %>% test(by = NULL, adjust = "sidak")

emmFF1$emmeans
emmFF2$emmeans
emmFF3$emmeans
emmFF3
```


#### **Figures**  

```{r message=FALSE, warning=FALSE, echo=FALSE}
library(survival)
library(survminer)
library(survMisc)
```

##### **Female Latency**  
  
Only **population** origin had a significant effect on female latency to forage. However, tutor population and the interaction between population and tutor population were included in the 'best' model.  
  
**Option 1**  
```{r, echo=FALSE}
# subsetting Females 
datasurv <- data_forage %>% filter(Sex == 'F') %>% na.omit

# create survival curve
fit <- survfit(Surv(Latency, event = event) ~ (Population + Tutor_pop), data = datasurv, na.action = "na.fail")

# plot survival curve
ggsurvplot(fit, conf.int = TRUE, fun = 'event',
           palette = c('lightskyblue', 'lightskyblue', 
                       'coral', 'coral'),
           censor = F,
           linetype= c('dotted', 'solid', 'dotted', 'solid'),
           ylab = 'Proportion of females that have foraged',
           xlab = 'Time (s)',
           legend = c(.8,0.3),
           legend.title = "Population/Tutor Population",
           legend.labs = c("HP/HP", "HP/LP", "LP/HP", "LP/LP"))

```

**Option 2** Currently in manuscript version  
```{r echo=FALSE}
# SAVED PDF

# create survival curve
fit2 <- survfit(Surv(Latency, event = event) ~ Population, data = datasurv, na.action = "na.fail")

# plot survival curve
ggsurvplot(fit2, conf.int = TRUE, fun = 'event',
           palette = c('black', 'grey'),
           censor = F,
           ylab = 'Proportion of females that have foraged',
           xlab = 'Time (s)',
           legend = c(.8,0.3),
           legend.title = "Source Population", 
           legend.labs = c("HP","LP"))




fig1 <- dataf %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  group_by(Population, Tutor_pop) %>%
  ggplot(aes(y = Latency, x = Population)) +
    stat_summary(fun = mean, geom = "point") +
    stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12))

fig1



```

**Option 3**  
```{r echo=FALSE}
library(ggplot2)
dataf <- data_forage %>%
  filter(Sex == 'F') %>%
  na.omit

fig1 <- dataf %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  group_by(Population, Tutor_pop) %>%
  ggplot(aes(y = Latency, x = Population, group = Tutor_pop, col = Tutor_pop)) +
    stat_summary(fun = mean, geom = "point") +
    stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12))

fig1
```
  
**Option 4**  
```{r echo=FALSE}

# SAVED PDF
fig1 <- dataf %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  group_by(Population, Tutor_pop) %>%
  ggplot(aes(y = Latency, x = Tutor_pop, group = Population, col = Population)) +
    stat_summary(fun = mean, geom = "point") +
    stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12))

fig1

```

##### **Male Latency**  
  
**Predation** and there interaction between **Predation** and **Population** origin had a significant effect on male latency to forage. 
  
**Option 1** Currently in manuscript version  
```{r echo=FALSE}
# subsetting Males
datasurv2 <- data_forage %>%  filter(Sex == 'M') %>%  na.omit

# create survival curve
fit2 <- survfit(Surv(Latency, event = event) ~ Population + Pred, data = datasurv2, na.action = "na.fail")

# plot survival curve
# SAVED PLOT
ggsurvplot(fit2, conf.int = TRUE, fun = 'event',
           palette = c('black', 'black', 
                       'grey', 'grey'),
           censor = F,
           linetype= c('dotted', 'solid', 'dotted', 'solid'),
           ylab = 'Proportion of males that have foraged',
           xlab = 'Time (s)',
           legend = c(.8,0.3),
           legend.title = "Population/Rearing Water",
           legend.labs = c("HP/pred-", "HP/pred+", "LP/pred-",
                           "LP/pred+"))
```

**Option 2**  
```{r echo=FALSE}
fit3<- survfit(Surv(Latency, event = event)~Pred, data = datasurv2, na.action = 'na.fail')

ggsurvplot(fit3, conf.int = T, fun = 'event')
```

**Option 3**  
```{r echo=FALSE}
fit4<- survfit(Surv(Latency, event = event)~Population, data = datasurv2, na.action = 'na.fail')

ggsurvplot(fit4, conf.int = T, fun = 'event')
```

**Option 4**  
```{r echo=FALSE}
datam <- data_forage %>%
  filter(Sex == 'M') %>%
  na.omit

#SAVED PDF
fig1 <- datam %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male")) %>%
  ggplot(aes(y = Latency, x = Pred, group = Population, col = Population)) +
    stat_summary(fun = mean, geom = "point") +
    stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12))

fig1

```

**Option 5**  
```{r echo=FALSE}
library(ggplot2)


fig1 <- datam %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  ggplot(aes(y = Latency, x = Population, group = Pred, col = Pred)) +
    stat_summary(fun = mean, geom = "point") +
    stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12))

fig1

```

**Option 6**  
This includes all the variables for latency that are in the model, but it is just so hard to comprehend, that I think we go with the simplified version above that shows the significant relationships  
```{r echo=FALSE}
library(ggplot2)
datam <- data_forage %>%
  filter(Sex == 'M') %>%
  na.omit


fig2 <- datam %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  group_by(Pred, Tutor_pop) %>%
  ggplot(aes(y = Latency, x = Water, group = Pred_Tutor, col = Pred, linetype = Tutor_pop)) +
    stat_summary(fun = mean, geom = "point") +
    stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
  facet_grid(~Population) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    labs(col = "Raising Environment", linetype ="Tutor Origin") +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12))

fig2

```

##### **Female Attempts**  
  
**Population**, **Tutor Population**, and **Test Water**, and the interaction between **Rearing Water** and **Test Water** had significant effects on female foraging attempts.


```{r}
fig1 <- dataf %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  group_by(Population, Tutor_pop) %>%
  ggplot(aes(y = Attempts, x = Population)) +
    stat_summary(fun = mean, geom = "point") +
    #stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12)) 

fig1

fig2 <- dataf %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  ggplot(aes(y = Attempts, x = Tutor_pop)) +
    stat_summary(fun = mean, geom = "point") +
    #stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12))

fig2

fig3 <- dataf %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  ggplot(aes(y = Attempts, x = Water)) +
    stat_summary(fun = mean, geom = "point") +
    #stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12))

fig3

fig4 <- dataf %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  ggplot(aes(y = Attempts, x = Water, col = Pred)) +
    stat_summary(fun = mean, geom = "point") +
    stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12))

fig4

par(mfrow=c(2,2))
fig1
fig2
fig3
fig4

```

```{r}

fig2 <- dataf %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  group_by(Population, Tutor_pop) %>%
  ggplot(aes(y = Attempts, x = Population, group = Tutor_pop, col = Tutor_pop)) +
    stat_summary(fun = mean, geom = "point") +
    #stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12))

fig2

fig3 <- dataf %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  group_by(Population, Tutor_pop) %>%
  ggplot(aes(y = Attempts, x = Population, group = Water, col = Water)) +
    stat_summary(fun = mean, geom = "point") +
    #stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12))

fig3
```



**Option 1** Currently in manuscript version   
```{r warning=FALSE, message=FALSE, echo=FALSE}
library(ggplot2)
dataf <- data_forage %>% filter(Sex == 'F') %>% na.omit
fig3 <- dataf %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  group_by(Pred) %>%
  ggplot(aes(y = Attempts, x = Water, group = interaction(Population, Tutor_pop), col = Population, linetype = Tutor_pop)) +
    stat_summary(fun = mean, geom = "point") +
    stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
  #facet_grid(~Population) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    #labs(col = "Raising Environment", linetype ="Tutor Origin") +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12)) +
  ylab('Female foraging attempts') +
  xlab('Test water')

fig3 ####save and in manuscript

```

**Option 2**  
```{r echo=FALSE}
fig <- dataf %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  group_by(Pred) %>%
  ggplot(aes(y = Attempts, x = Pred, group = interaction(Population,Water), col = Population, linetype = Water)) +
    stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1)

fig
```
  
**Option 3**  
```{r echo=FALSE}
library(ggplot2)
dataf <- data_forage %>%
  filter(Sex == 'F') %>%
  na.omit


fig3 <- dataf %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  group_by(Population, Tutor_pop) %>%
  ggplot(aes(y = Attempts, x = Population, group = Water, col = Water)) +
    stat_summary(fun = mean, geom = "point") +
    stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12))

fig3

```
  
##### **Male Attempts**  
  
Only the interaction between **Tutor Population** and **Test Water** had significant effects on male foraging attempts.
  
**Option 1** Currently in manuscript version  
```{r echo=FALSE}
library(ggplot2)
datam <- data_forage %>%
  filter(Sex == 'M') %>%
  na.omit


fig4 <- datam %>%
  mutate(Tutor_pop = recode(Tutor_pop, "AH" = "HP", "AL" = "LP"),
         Population = recode(Population, "AH" = "HP", "AL" = "LP"),
         Sex = recode(Sex, "M" = "Male", "F" = "Female")) %>%
  group_by(Population, Tutor_pop) %>%
  ggplot(aes(y = Attempts, x = Water, group = Tutor_pop, col = Tutor_pop)) +
    stat_summary(fun = mean, geom = "point") +
    stat_summary(fun = mean, geom = "line") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.1) +
    theme_bw() + scale_colour_grey(start = 0, end = 0.7) +
    theme(strip.background = element_blank(),
          strip.text.x = element_text(size = 15),             strip.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12)) +
  ylab('Male foraging attempts') +
  xlab('Test water')

fig4 #in manuscript

```
